---
title: "1. Datos, Modelos y Software. Ejercicios"
date: "Enero 2025"
output: 
  html_document:
    toc: true
    toc_depth: 1
    theme: cerulean
---


<style>
body {
text-align: justify}
</style>

<style type="text/css">
body{/*Normal*/
     font-size: 20px;
}
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(discrtr) # A companion package for the book Introduction to Discrete Choice Analysis with `R`
library(mlogit) # Multinomial Logit Models
library(readr) # Read Rectangular Text Data
```



Invoke data set Mode from package mlogit. To do this you need to first load the package. This is a data set with choices about mode of transportation. This is done as follows:

```{r}
data("Mode")
```

Once you have loaded the data set, answer the following questions:
Describe this data set. How many variables are there and of which type (i.e., categorical/quantitative)?


How many different modes of transportation are in this data set? What is the most popular mode? What is the least popular mode?

In general, what is the most expensive mode? The least expensive?

Create a plot showing the univariate distributions of time by car and time by bus. Discuss.

How do choices relate to cost by the different modes?





