---
title: "2. Exploratory Data Analysis. Ejercicios"
date: "Febrero 2025"
output: 
  html_document:
    toc: true
    toc_depth: 1
    theme: cerulean
---


<style>
body {
text-align: justify}
</style>

<style type="text/css">
body{/*Normal*/
     font-size: 20px;
}
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(discrtr) # A companion package for the book Introduction to Discrete Choice Analysis with `R`
library(mlogit) # Multinomial Logit Models
library(readr) # Read Rectangular Text Data

library(gplots) # Various R Programming Tools for Plotting Data
library(ggmosaic) # Mosaic Plots in the 'ggplot2' Framework
library(treemapify)
library(ggridges)
library(ggalluvial)
library(plotly)
```


Call data set Car from package mlogit. Once you have loaded the data set, do the following:

* How many variables are there in this data set and of which type (i.e., categorical/quantitative)?

* Choose four relevant categorical variables from this data set and describe them using univariate, bivariate, and multivariate techniques. Discuss your results.

* What ideas about individuals’ choices regarding car do you develop from this EDA exercise?


Se carga el conjunto de datos, se muestran las variables y su tipo:

```{r}
data(Car)
glimpse(Car)
```




En este caso es necesario añadir columnas acerca de la elección:


```{r}
new_car <- Car
choice_char <- gsub("choice","", new_car$choice)
new_car <- new_car |> mutate(choice_char = choice_char)

type <- vector("character", nrow(new_car))
fuel <- vector("character", nrow(new_car))
price <- vector("numeric", nrow(new_car))
range <- vector("numeric", nrow(new_car))
acc <- vector("numeric", nrow(new_car))
speed <- vector("numeric", nrow(new_car))
pollution <- vector("numeric", nrow(new_car))
size <- vector("numeric", nrow(new_car))
space <- vector("numeric", nrow(new_car))
cost <- vector("numeric", nrow(new_car))
station <- vector("numeric", nrow(new_car))
for (i in 1:nrow(new_car)) {
  type[i] <- as.character(new_car[i, paste0("type", new_car$choice_char[i], collapse = "")])
  fuel[i] <- as.character(new_car[i, paste0("fuel", new_car$choice_char[i], collapse = "")])
  price[i] <- new_car[i, paste0("price", new_car$choice_char[i], collapse = "")]
  range[i] <- new_car[i, paste0("range", new_car$choice_char[i], collapse = "")]
  acc[i] <- new_car[i, paste0("acc", new_car$choice_char[i], collapse = "")]
  speed[i] <- new_car[i, paste0("speed", new_car$choice_char[i], collapse = "")]
  pollution[i] <- new_car[i, paste0("pollution", new_car$choice_char[i], collapse = "")]
  size[i] <- new_car[i, paste0("size", new_car$choice_char[i], collapse = "")]
  space[i] <- new_car[i, paste0("space", new_car$choice_char[i], collapse = "")]
  cost[i] <- new_car[i, paste0("cost", new_car$choice_char[i], collapse = "")]
  station[i] <- new_car[i, paste0("station", new_car$choice_char[i], collapse = "")]
}

new_car <- new_car |> mutate(choice_num= factor(choice_char), type=type, fuel=fuel, price=price, range=range,
                             acc=acc, speed=speed, pollution=pollution, size=size, space=space, cost=cost,
                             station=station)

new_car$type <- factor(new_car$type, levels = levels(new_car$type1))
new_car$fuel <- factor(new_car$fuel, levels = levels(new_car$fuel1))
```
